Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/2_method.tex
fix figure 1 and 2

% !TEX root =  paper.tex
\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser-image.png}
	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation. We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.\TODO{Is it possible to have the weights next to the lines?}}
	\label{fig:teaser_pipeline}
\end{figure}
\section{Method}
%\begin{figure*}[t!]
%	\begin{center}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

>>>>

% !TEX root =  paper.tex
\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation. We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.}
	\label{fig:teaser_pipeline}
\end{figure}
\section{Method}
%\begin{figure*}[t!]
%	\begin{center}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}
